\subsection{Guidelines for Developers}\label{sec:guidelines}
\begin{comment}
\end{comment}

In this subsection, we discuss guidelines for IoT developers based on our
observed results. In fact, Hackster provides developers with initial guidelines
on how to properly write a page for an IoT project~\cite{guidelines}. Our
observed results could be used to improve the guidelines provided by Hackster.

{\bfseries Pictures.} The guidelines provided by Hackster are mostly related to
improving the page of a project. The guidelines mention that the ``cover
picture'' of a project should be of high resolution and should show the end
result of the project.  Based on our results, the guidelines could mention that
additional pictures on the project description will likely increase the
popularity of the project. 

{\bfseries Tags.} The Hackster guidelines also mention that tags should be
limited to a maximum of 3 and that tag descriptions such as ``Arduino'' or
``Raspberry Pi'' should be avoided. Nonetheless, our results reveal that as the
number of tags increases, the popularity of a project is likely to increase.
In addition, we observe that tag descriptions such as ``Arduino'' or
``Raspberry Pi'' are associated with popular projects, which contradicts the
current guidelines.

{\bfseries Code.} The current Hackster guidelines are very brief when it comes
to the code of a project. The guidelines mention that the proper language
should be selected for code files and that no placeholders should be used.
Based on our results, the guidelines could also mention that the code of a
project should be as compact as possible (\ie{} less lines of code is
desirable). Also, code comments and modularity should also be encouraged in the
guidelines.

{\bfseries Developer profiles \& actions.} The current Hackster guidelines are
oblivious to the actions or profiles of developers. The guidelines could be
improved by including our empirical observations regarding the aspects involving
developers. For example, mentioning that developers should promptly reply users
could improve the guidelines. Additionally, developers should be encouraged to
write rich biographies, since we observe that a lengthier biography is
associated with popular IoT projects.



