\begin{comment}
\end{comment}
\subsection*{\bfseries\RQtwo}

\input{Tables/RQ2.tex}

\noindent\textbf{\textit{Motivation.}} As the value of user comments is unknown
for all developers, a developer may neglect user comments or, on the other
hand, pay too much attention to user comments. In this research question, we
study user comments with respect to $20$ metrics that measure various angles of
comments (see Section~\ref{sec:measure}) to help developers understand the
metrics that are important to achieve a better project popularity. We show that
developers should care about users' comments.

\noindent\textbf{\textit{Contribution of the User Comments Group of Metrics.}}
\textbf{The comments posted by users make a significant contribution to the
popularity of IoT projects}. The collected metrics for the {\em user comments}
group play an important role in explaining the popularity of IoT projects as
the $\chi^2$ test denotes a $Pr(>\chi)<2.2E-16$.

\noindent\textbf{\textit{Significant Metrics.}} Table~\ref{table:RQ2} shows the
list of the {\em user comments} metrics along with the correlated metrics.

\textbf{The sentiment scores of the comments are significantly related to the
popularity of IoT projects.} As shown in Table~\ref{table:RQ2}, Our model
suggests the higher the comments with positive sentiment scores, the higher
project popularity. On the other hand, the higher the comments with negative
scores, the lower projects popularity.

\textbf{Answering questions is positively associated with the popularity of IoT
projects.} The number of questions that are replied by project developers
shares a significant positive relationship with project popularity. However, as
the number of questions increases, the popularity of projects tends to
decrease.  Developers should avoid an increase in the number of questions by
addressing the potential issues that may be reflected in the questions.
Conversely, replying to the non-question comments does not share a significant
relationship with the popularity of projects.

\hypobox{The user comments share a significant relationship with the popularity
of projects. Developers should avoid leaving unanswered questions in order to
achieve a better project popularity.}

