\noindent \textbf{\RQfive}




\vspace{0.1cm}

\noindent\textbf{\textit{Motivation.}} 
Developers' activities may be interpreted as ``distracting'' or useful~\cite{leonardi2013enterprise}. Developers do not know how much their activities can contribute to the popularity of their projects. We observe that developers' activities can improve the popularity of the associated projects significantly.

\vspace{0.1cm}

\noindent\textbf{\textit{Contribution of the Developer Activities Group of Metrics.}} \textbf{The developer activities group of metrics contributes to project popularity significantly.} The $\chi^2$ test indicates a $Pr(>\chi)=4.38E-3$. Thereby, project developers should be active in online communities, such as Hackster, to achieve a higher project popularity.

\vspace{0.1cm}

\input{Tables/RQ5.tex}

\noindent\textbf{\textit{Significant Metrics.}} Table~\ref{table:RQ5} shows the
list of metrics that are related to the {\em developer activities} group of metrics.

\textbf{As the number of followings of a developers increases, project popularity increases.} There is a significant positive relationship between the number of followings and project popularity. In social media, as the number of followings increases, users react by checking the follower's profile~\cite{kwak2010twitter,postill2012social}. Therefore, the relationship between the number of followings and project popularity may be the result of such a phenomenon in social media.

\hypobox{The developer activities group of metrics make a significant contribution to explaining project popularity. The activities include following other users, posting comments, and giving `likes' to other users' posts.}

